Maximum Entropy Spectral Analysis: a case study

### 2021-03-31 paper/mesa.tex
Removed seismic stuff
Cited rationale of MAXENT

An appealing alternative approach, based on the Maximum Entropy principle \cite{JaynesArticle,jaynes2003ptl}, has been put forward by Burg \cite{burg1975maximum}. Being rooted on solid theoretical foundations, we will see that Burg's method, unlike Welch's, does not require any preprocessing of the data and requires very little tuning of the arbitrary parameters, as it provides an iterative closed form expression for the spectrum of a stochastic stationary time series. Furthermore, it embeds the PSD estimation problem into an elegant theoretical framework and makes minimal assumptions on the nature of the data.
Lastly and most importantly, it provides a robust link between spectral density estimation and the field of autoregressive processes. This provide a natural and simple machinery to forecast a time series, thus predicting past observations based on previous ones.

@@

\subsection{Seismic waveforms} \label{sec:seismic_timeseries}
\blindtext

\cite{seismic_data}\\
Are data non stationary??\\
Cosa sono i picchi?\\
Che cos'è la time series che guardiamo?

\blindtext

\begin{figure}
	\caption{Do a caption}
	\label{fig:seismic_spectrum}
	\includegraphics{Images/seismic_plots/seismic_spectrum.pdf}
\end{figure}

\begin{figure}
	\caption{Do a caption}
	\label{fig:seismic_forecast}
	\includegraphics{Images/seismic_plots/forecast_accuracy.pdf}
\end{figure}

>>>>

An appealing alternative approach, based on the Maximum Entropy principle \cite{JaynesArticle,jaynes2003ptl, Jaynes_MAXENT}, has been put forward by Burg \cite{burg1975maximum}. Being rooted on solid theoretical foundations, we will see that Burg's method, unlike Welch's, does not require any preprocessing of the data and requires very little tuning of the arbitrary parameters, as it provides an iterative closed form expression for the spectrum of a stochastic stationary time series. Furthermore, it embeds the PSD estimation problem into an elegant theoretical framework and makes minimal assumptions on the nature of the data.
Lastly and most importantly, it provides a robust link between spectral density estimation and the field of autoregressive processes. This provide a natural and simple machinery to forecast a time series, thus predicting past observations based on previous ones.

@@
